Introducing Distributed Dynamic Data-intensive (D3) Science: Understanding Applications and Infrastructure

### 2016-08-20 3dpas_intro.tex
consistent spelling of cyber-infrastructure

\item In \S\ref{sec:infrastructure}, we subsequently describe the software/systems infrastructure used to support the distributed and dynamic characteristics of applications in \S\ref{sec:scenarios}. We outline support for data management, analysis, and coordination, providing examples of actual Cyberinfrastructure made use of by our surveyed applications for these purposes.

>>>>

\item In \S\ref{sec:infrastructure}, we subsequently describe the software/systems infrastructure used to support the distributed and dynamic characteristics of applications in \S\ref{sec:scenarios}. We outline support for data management, analysis, and coordination, providing examples of actual cyberinfrastructure made use of by our surveyed applications for these purposes.
